A Bidirected String Graph Model of Genome Assembly

### 2012-11-29 presentation/presentation.tex
Another build graph slide

\usepackage{graphicx}
\usepackage{listings}
\usepackage{comment}
\usepackage{float}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}

@@

@@

		\item We must allow each read to be used either in the
		reverse-complement or forward direction.
		\item Therefore, we must allow the edges to be traversed in either
		direction.
		\item However, each read must still be used in a consistent way within
		any single assembly.
		\item Solution: use a {\bf bidirected graph}.
	\end{itemize}
\end{frame}

@@

>>>>

\usepackage{graphicx}
\usepackage{listings}
\usepackage{comment}
\usepackage{float}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{multicol}

@@

\begin{frame}{Build the fragment string assembly graph (cont.)}
	\begin{itemize}
		\item Consider three reads $f$, $g$, and $h$, that overlap as follows:
	\end{itemize}
	\vspace{-0.4cm}
	\begin{center}
		\begin{tikzpicture}[>=\ReadArrowType]
			\draw[->,style=very thick] (0,   0.6) node[anchor=east] {f} -- (3.0, 0.6);
			\draw[->,style=very thick] (1.0, 0.3) node[anchor=east] {g} -- (4.0, 0.3);
			\draw[<-,style=very thick] (2.0, 0.0) node[anchor=east] {h} -- (5.0, 0.0);
		\end{tikzpicture}
	\end{center}
	\vspace{-0.5cm}
	\begin{itemize}
		\item {There are 3 overlaps so there will be 3 edges, and we'd like for
		the graph to allow exactly the following four walks:}
		\vspace{-0.3cm}
		\begin{multicols}{2}
			\begin{itemize}
				\item $f \to g \to h$
				\item $h \to g \to f$
				\item $f \to h$
				\item $h \to f$
			\end{itemize}
		\end{multicols}
	\end{itemize}
	\begin{tabular}{ccp{3.3cm}}
		{\small Undirected graph?}
			&
			\begin{tikzpicture}[>=triangle 45]
				\tikzstyle{every node} = [circle,fill=blue!20,draw=black];
				\node (f) at (0, 0) {f};
				\node (g) at (1.7, 0) {g};
				\node (h) at (3.4, 0) {h};
				\draw[-,style=very thick] (f) edge (g);
				\draw[-,style=very thick] (g) edge (h);
				\draw[-,style=very thick,bend left] (f) edge (h);
			\end{tikzpicture}
			& 
			\vspace{-0.8cm}
			{\footnotesize No; nothing indicates we can't walk \mbox{$g \to h \to
			f$}.}
			\\
		{\small Directed graph?}
			&
			\begin{tikzpicture}[>=triangle 45]
				\tikzstyle{every node} = [circle,fill=blue!20,draw=black];
				\node (f) at (0, 0) {f};
				\node (g) at (1.7, 0) {g};
				\node (h) at (3.4, 0) {h};
				\draw[->,style=very thick] (f) edge (g);
				\draw[->,style=very thick] (g) edge (h);
				\draw[->,style=very thick,bend left] (f) edge (h);
			\end{tikzpicture}
			&
			\vspace{-0.8cm}
			{\footnotesize
				No; this doesn't allow the walks $h \to g \to f$ and $h \to f$.}
			\\
	\end{tabular}
\end{frame}

@@

		\item We must allow each read to be used either in the
		reverse-complement or forward direction.
		\item We must allow the edges to be traversed in either direction.
		\item However, each read must still be used in a consistent way within
		any single assembly.
		\item Solution: use a {\bf bidirected graph}.
	\end{itemize}
	\begin{center}
		\begin{tikzpicture}[>=triangle 45]
			\tikzstyle{every node} = [circle,fill=blue!20,draw=black];
			\node (f) at (0, 0) {f};
			\node (g) at (1.7, 0) {g};
			\node (h) at (3.4, 0) {h};
			\draw[>->,style=very thick] (f) edge (g);
			\draw[>-<,style=very thick] (g) edge (h);
			\draw[>-<,style=very thick,bend left] (f) edge (h);
		\end{tikzpicture}
	\end{center}
\end{frame}

@@

%\begin{frame}{Walking through the bidirected string graph (cont.)}
	%\begin{minipage}{0.5\textwidth}
		%\begin{tikz
	%\end{minipage}
%\end{frame}
